SMT-Boosted Security Types for Low-Level MPC

### 2025-04-26 esop25/slides.tex
checkpoint

Verifying equational properties 
$$    
  \inferrule[Encode]
  {\eqs \models \phi \eop \phi' \oplus \rx{w}{\cid} \\
   \oplus \in \{ \fplus,\fminus \}\\
   \eqj{R}{\eqs}{\phi'}{\ty}}
  {\eqj{R;\{ \rx{w}{\cid} \}}{\eqs}{\phi}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}
$$

>>>>

  Verifying equational properties also supports verification of confidentiality.
  It is well-known that expressions of the form:
  $$
  e - \rx{w}{\cid}
  $$
  are a means of encrypting $e$ using $\rx{w}{\cid}$ as a one-time-pad in any
  size field. This can be leveraged in typing. 
  $$    
  \inferrule[Encode]
  {\eqs \models \toeq{e} \eop \toeq{e'} - \rx{w}{\cid}\\
   \eqj{R}{\eqs}{e'}{\ty}}
  {\eqj{R;\{ \rx{w}{\cid} \}}{\eqs}{e}{\setit{\cty{\rx{w}{\cid}}{\ty}}}}
  $$
  \begin{itemize}
  \item The \emph{ciphertype} $\cty{\rx{w}{\cid}}{\ty}$ indicates the computation
    results in a value encrypted with $\rx{w}{\cid}$.
  \item $\ty$ is a conservative approximation of the dependencies in $e'$.
  \item The \emph{randomness environment} $R;\{ \rx{w}{\cid} \}$ enforces
    linearity.
  \end{itemize}
